Group 9 Paper

### 2021-12-16 paper.Rmd
fIXED ECHO

```{r LDA}
LDA_model = lda(HeartDisease~., data=train)
LDA_model

@@

```{r message=FALSE, warning=FALSE}
train_matrix <- model.matrix(HeartDisease ~ ., data = train)
test_matrix <- model.matrix(HeartDisease ~ ., data = test)
grid <- 10^seq(10, -2, length=100)
lasso <- glmnet(train_matrix, train$HeartDisease, alpha = 1, lambda = grid, thresh = 1e-12, family = "binomial")
#plot(lasso)
cv_lasso  <- cv.glmnet(train_matrix, train[, "HeartDisease"], alpha=1,family = "binomial")
#plot(cv_lasso)
best_lambda_lasso <- cv_lasso$lambda.min
lasso_prediction <- predict(lasso, newx = test_matrix, s = best_lambda_lasso)
lasso_MSE <- mean((lasso_prediction - test[, "HeartDisease"])^2)
num_zeros <-cv_lasso$nzero[which.min(cv_lasso$cvm)]
# MSE values to use:
paste("Tuning Lambda",best_lambda_lasso)
#lasso_MSE
#paste("Number of zeros",num_zeros)
#Confusion Matrix
predicted_lasso <- predict(lasso, newx= test_matrix, s=best_lambda_lasso)
predicted_lasso <- ifelse(predicted_lasso>0.5,1,0)
confm_lasso<-table(predicted=predicted_lasso,True=test$HeartDisease)
confm_lasso
#Over all correct:
overall_lasso <- (confm_lasso[1,1]+confm_lasso[2,2])/sum(confm_lasso)
kable(confm_lasso) #confusion matrix
overall_lasso #over all correct
```

@@

In the paper Banerjee, et al. discuss how to choose the most representative tree in an ensemble, which is done by finding the average distance between one tree and all other trees in the ensemble. Banerjee, et al. discusses several types of distance in this paper only one of them was used, as it was already implemented in a R package. This measure captures the similarities between the predictions, in that 2 trees are similar if they have the same predictions for all subjects, this is defined by Banerjee, et al as :
$d_2(T_1,T_2)=\frac{1}{n}\sum_{i=1}^n(\hat{y}_{1i}-\hat{y}_{2i})^2$, if the trees perfectly similar, the distance $d_2(T_1,T_2)$ is equal 0. For for finding the representative tree we used the package "reptree", and using it on this random forests we got the following tree:

@@

```{r SVM_linear}
svm_linear_cv = tune(svm, HeartDisease~., scale=TRUE, kernel="linear", data=train,
                      ranges = list(cost = seq(0.1, 5, by = 0.1)))

@@

```{r SVM_poly}
svm_poly_cv = tune(svm, HeartDisease~., scale=TRUE, kernel="polynomial", data=train,
                      ranges = list(cost = seq(0.1, 5, by = 0.1),
                                    degree = c(2,3,4, 5)))

@@

```{r SVM_radial}
train <- read.csv("train.csv")
test <- read.csv("test.csv")
train$ChestPainType <- as.factor(train$ChestPainType)
train$Sex <- as.factor(train$Sex)
train$FastingBS <- as.factor(train$FastingBS)
train$RestingECG <- as.factor(train$RestingECG)
train$ExerciseAngina <- as.factor(train$ExerciseAngina)
train$ST_Slope <- as.factor(train$ST_Slope)
test$ChestPainType <- as.factor(test$ChestPainType)
test$Sex <- as.factor(test$Sex)
test$FastingBS <- as.factor(test$FastingBS)
test$RestingECG <- as.factor(test$RestingECG)
test$ExerciseAngina <- as.factor(test$ExerciseAngina)
test$ST_Slope <- as.factor(test$ST_Slope)

@@

```{r}
library(knitr)
df1 = data.frame(Method = c("Logistic Regression","LDA","KNN","LASSO","Bagging","Random Forest","Boosting","SVM"),  Accuracy= c(overall_logit,overall_LDA,overall_knn_1,overall_lasso,overall_bag,overall_RF,overall_boost,overall_SVM))

@@

We found that all of our models, except KNN, had an accuracy within a few points. It was interesting to note from LDA that our prior probabilities of our two classes closely follow the CDCs probability of getting heart disease. ST-Slope was shown to be the most important predictor in most of our models and we estimate this is the reason for the similar accuracy between models. So choosing the best model depends a lot on whether or not we value more inference or prediction, if we only care about inference, boosting is probably the best method otherwise, something like the logistic regression might be more useful for inference, however, if both are really important a using a random forest with a representative tree might be the best way.

>>>>

```{r LDA,echo=FALSE}
LDA_model = lda(HeartDisease~., data=train)
LDA_model

@@

```{r message=FALSE, warning=FALSE,echo=FALSE}
train_matrix <- model.matrix(HeartDisease ~ ., data = train)
test_matrix <- model.matrix(HeartDisease ~ ., data = test)
grid <- 10^seq(10, -2, length=100)
lasso <- glmnet(train_matrix, train$HeartDisease, alpha = 1, lambda = grid, thresh = 1e-12, family = "binomial")
#plot(lasso)
cv_lasso  <- cv.glmnet(train_matrix, train[, "HeartDisease"], alpha=1,family = "binomial")
#plot(cv_lasso)
best_lambda_lasso <- cv_lasso$lambda.min
lasso_prediction <- predict(lasso, newx = test_matrix, s = best_lambda_lasso)
lasso_MSE <- mean((lasso_prediction - test[, "HeartDisease"])^2)
num_zeros <-cv_lasso$nzero[which.min(cv_lasso$cvm)]
# MSE values to use:
paste("Tuning Lambda",best_lambda_lasso)
#lasso_MSE
#paste("Number of zeros",num_zeros)
#Confusion Matrix
predicted_lasso <- predict(lasso, newx= test_matrix, s=best_lambda_lasso)
predicted_lasso <- ifelse(predicted_lasso>0.5,1,0)
confm_lasso<-table(predicted=predicted_lasso,True=test$HeartDisease)
confm_lasso
#Over all correct:
overall_lasso <- (confm_lasso[1,1]+confm_lasso[2,2])/sum(confm_lasso)
kable(confm_lasso) #confusion matrix
overall_lasso #over all correct
```

@@

In the paper Banerjee, et al. discuss how to choose the most representative tree in an ensemble, which is done by finding the average distance between one tree and all other trees in the ensemble. Banerjee, et al. discusses several types of distance in this paper only one of them was used, as it was already implemented in a R package. This measure captures the similarities between the predictions, in that 2 trees are similar if they have the same predictions for all subjects, this is defined by Banerjee, et al as :
$d_2(T_1,T_2)=\frac{1}{n}\sum_{i=1}^n(\hat{y}_{1i}-\hat{y}_{2i})^2$, if the trees perfectly similar, the distance $d_2(T_1,T_2)$ is equal 0. Finding the representative tree was done by using the package "reptree", and using it on this random forests we got the following tree:

@@

```{r SVM_linear,echo=FALSE}
svm_linear_cv = tune(svm, HeartDisease~., scale=TRUE, kernel="linear", data=train,
                      ranges = list(cost = seq(0.1, 5, by = 0.1)))

@@

```{r SVM_poly,echo=FALSE}
svm_poly_cv = tune(svm, HeartDisease~., scale=TRUE, kernel="polynomial", data=train,
                      ranges = list(cost = seq(0.1, 5, by = 0.1),
                                    degree = c(2,3,4, 5)))

@@

```{r SVM_radial,echo=FALSE}
train <- read.csv("train.csv")
test <- read.csv("test.csv")
train$ChestPainType <- as.factor(train$ChestPainType)
train$Sex <- as.factor(train$Sex)
train$FastingBS <- as.factor(train$FastingBS)
train$RestingECG <- as.factor(train$RestingECG)
train$ExerciseAngina <- as.factor(train$ExerciseAngina)
train$ST_Slope <- as.factor(train$ST_Slope)
test$ChestPainType <- as.factor(test$ChestPainType)
test$Sex <- as.factor(test$Sex)
test$FastingBS <- as.factor(test$FastingBS)
test$RestingECG <- as.factor(test$RestingECG)
test$ExerciseAngina <- as.factor(test$ExerciseAngina)
test$ST_Slope <- as.factor(test$ST_Slope)

@@

```{r,echo=FALSE}
library(knitr)
df1 = data.frame(Method = c("Logistic Regression","LDA","KNN","LASSO","Bagging","Random Forest","Boosting","SVM"),  Accuracy= c(overall_logit,overall_LDA,overall_knn_1,overall_lasso,overall_bag,overall_RF,overall_boost,overall_SVM))

@@

We found that all of our models, except KNN, had an accuracy within a few points as we can see from the table above. It was interesting to note from LDA that our prior probabilities of our two classes closely follow the CDCs probability of getting heart disease. ST-Slope was shown to be the most important predictor in most of our models and we estimate this is the reason for the similar accuracy between models. So choosing the best model depends a lot on whether or not we value more inference or prediction, if we only care about inference, boosting is probably the best method otherwise, something like the logistic regression might be more useful for inference. However, if both are really important a using a random forest with a representative tree might be the best way, it allows us to lose some predictive performance from boosting in order to gain the ability to do some interpretation.
